---
title: "Iteration and List Columns"
output: github_document
---

I'm an R Markdown document! 
load packages
```{r}
library(tidyverse)
library(rvest)
```

setup
```{r}
knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "right"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

```

set seed
```{r}
set.seed(12345)
```

### Lists
```{r}
vec_numeric = 1:4
vec_char = c("my", "name", "is", "jeff")

tibble(
  num = vec_numeric,
  char = vec_char
)
```

Diff stuff with diff lengths
letters is all of the letters
```{r}
l = list(
  vec_numeric = 1:5,
  vec_char = LETTERS,
  matrix = matrix(1:10, nrow = 5, ncol = 2),
  summary = summary(rnorm(100))
)


```

Accessing lists
$ general way to access elements in a list; ok to use $ here for lists just not for dfs

```{r}
l$vec_char
l[[2]]
l[["summary"]]

```

### loops
here each element is a collection of numbers
```{r}
list_norm_samples =
  list(
    a = rnorm(20, 1, 5),
    b = rnorm(20, 0, 7),
    c = rnorm(20, 20, 1),
    d = rnorm(20, -45, 13)
  )
```

let's compute the mean and sd for each collection of numbers

```{r}
mean_and_sd = function(x) {
  
    if (!is.numeric(x)) {
    stop("Argument should be numbers")
  } else if (length(x) < 2) {
    stop("Need at least 2 numbers to get z scores")
  }
  
  mean_x = mean(x)
  sd_x = sd(x)
  
  tibble(
    mean = mean_x,
    sd = sd_x
  )
}
```


```{r}
mean_and_sd(list_norm_samples$a)
mean_and_sd(list_norm_samples$b)
mean_and_sd(list_norm_samples$c)
mean_and_sd(list_norm_samples$d)

```

make sure you use i in the correct places
here our output is a list
```{r}
output = vector("list", length = 4)

for (i in 1:4) {
  
  output[[i]] = mean_and_sd(list_norm_samples[[i]])
}

```

### use `map`

```{r}
output = map(list_norm_samples, mean_and_sd)
```






