---
title: "Writing Functions"
output: github_document
---

load packages
```{r}
library(tidyverse)
library(rvest)
```

setup
```{r}
knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "right"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

```


Set seed for reproducibility. (get same random numbers each time)

```{r}
set.seed(12345)
```


#### Z score function

Z scores substract the mean and divide by the SD.

```{r}
x_vec = rnorm(20, mean = 5, sd = 0.3)


```

Compute Z scores for x_vec

```{r}
(x_vec - mean(x_vec)) / sd(x_vec)
```


Function that produces Z scores
input collection of numbers; output collection of z scores

```{r}
z_score = function(x) {
  
  if (!is.numeric(x)) {
    stop("Argument should be numbers")
  } else if (length(x) < 2) {
    stop("Need at least 2 numbers to get z scores")
  }
  
  z = (x - mean(x)) /sd(x)
  
  z
}
```
z does not exist outside of the function
make sure argument names are unique from oher variable names in your enviro

Check that this works. Applying this function to the x_vec

```{r, error = TRUE}
z_score(x = x_vec)

```

Keep checking. See how these breaks. Some produce errors while some kind of work

```{r, error = TRUE}
z_score(x = 3)
```
get an NA


```{r, error = TRUE}
z_score(c("hello", "there"))
```
error message


```{r, error = TRUE}
z_score(iris)
```
error message; entire iris dataframe


```{r, error = TRUE}
z_score(c(TRUE, TRUE, FALSE))
```
error message

Update our function with conditionals

### Multiple outputs

Write a function that returns mean and sd from a sample of numbers

```{r}
mean_and_sd = function(x) {
  
    if (!is.numeric(x)) {
    stop("Argument should be numbers")
  } else if (length(x) < 2) {
    stop("Need at least 2 numbers to get z scores")
  }
  
  mean_x = mean(x)
  sd_x = sd(x)
  
  tibble(
    mean = mean_x,
    sd = sd_x
  )
}
```


Check that our function works

```{r}
mean_and_sd(x_vec)
```


### Multiple inputs

```{r}
x_vec = rnorm(n = 30, mean = 5, sd = 0.5)

tibble(
  mean = mean(x_vec),
  sd = sd(x_vec)
)

```

Write a function that uses n, a true mean, and true SD as inputs

```{r}
sim_mean_sd = function(n_obs, mu, sigma) {
  
  x_vec = rnorm(n = n_obs, mean = mu, sd = sigma)
  
  tibble(
    mean = mean(x_vec),
    sd = sd(x_vec)
  )
  
}


sim_mean_sd(n_obs = 30, mu = 5, sigma = 0.5)

sim_mean_sd(12, 24, 2)
```

function assigns by positional matching if you did not name anything; good practice to name your inputs

## LOTR words function example
```{r}
lotr_load_and_tidy = function(path = "data/LotR_Words.xlsx", cell_range, movie_name) {
  
  movie_df = 
    readxl::read_excel(path, range = cell_range) |>
    mutate(movie = movie_name) |> 
    janitor::clean_names() |> 
    pivot_longer(
      female:male,
      names_to = "sex",
      values_to = "words"
    ) |> 
    select(movie, everything())
  
  movie_df
  
}

lotr_df = 
  bind_rows(
    lotr_load_and_tidy(cell_range = "B3:D6", movie_name = "fellowship_ring"),
    lotr_load_and_tidy(cell_range = "F3:H6", movie_name = "two_towers"),
    lotr_load_and_tidy(cell_range = "J3:L6", movie_name = "return_king")
  )



```

Best to write your code first; see that it works; then copy and paste it into your function


### NSUDH example
nth() gives you the next number table entry
```{r}

nsduh_url = "http://samhda.s3-us-gov-west-1.amazonaws.com/s3fs-public/field-uploads/2k15StateFiles/NSDUHsaeShortTermCHG2015.htm"

nsduh_html = read_html(nsduh_url)

data_marj = 
  nsduh_html |> 
  html_table() |> 
  nth(1) |>
  slice(-1) |> 
  select(-contains("P Value")) |>
  pivot_longer(
    -State,
    names_to = "age_year", 
    values_to = "percent") |>
  separate(age_year, into = c("age", "year"), sep = "\\(") |>
  mutate(
    year = str_replace(year, "\\)", ""),
    percent = str_replace(percent, "[a-c]$", ""),
    percent = as.numeric(percent)) |>
  filter(!(State %in% c("Total U.S.", "Northeast", "Midwest", "South", "West")))


```

Write a function for inputting these tables!
think what are the htings that are changing each time; what do our arguments/inputs need to be

```{r}
nsduh_import = function(html, table_number, outcome_name) {

  html |> 
  html_table() |> 
  nth(table_number) |>
  slice(-1) |> 
  select(-contains("P Value")) |>
  pivot_longer(
    -State,
    names_to = "age_year", 
    values_to = "percent") |>
  separate(age_year, into = c("age", "year"), sep = "\\(") |>
  mutate(
    year = str_replace(year, "\\)", ""),
    percent = str_replace(percent, "[a-c]$", ""),
    percent = as.numeric(percent),
    outcome = outcome_name) |> 
  filter(!(State %in% c("Total U.S.", "Northeast", "Midwest", "South", "West")))
  
}

nsduh_import(html = nsduh_html, table_number = 1, outcome_name = "marj")

```












